Dominance Regions for Imaginary $\bfg$-vectors

### 2021-10-05 dominance_regions.tex
Finished explaining the bijection between compatible subsets.

  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
  \begin{corollary}\mbox{}
    \begin{enumerate}
      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
    \end{enumerate}
  \end{corollary}

  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta(H)_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta(V)_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.

>>>>

  Then the following result immediately follows from Lemma~\ref{le:shadow statistic recursion}.
  \begin{corollary}\mbox{}
    \label{cor:remote shadows}
    \begin{enumerate}
      \item Suppose the Dyck path $D$ is vertically-adapted to $c$ and let $D'=\mu_{1,c}(D)$ with $D'_2=\{v'_1,\ldots,v'_{a_1}\}$.
        For $H\subset D_1$, define $V'\subset D'_2$ by $V'=D'_2\setminus \mu_{1,c}(H)$.
        Then, for $1 \le d < j \le a_1$, we have $|\rsh_D(H)_{j;d}|=|\rsh_{D'}(V')_{d;j}|$.
      \item Suppose the Dyck path $D$ is horizontally-adapted to $b$ and let $D''=\mu_{2,b}(D)$ with $D''_1=\{h''_1,\ldots,h''_{a_2}\}$.
        For $V\subset D_2$, define $H''\subset D''_1$ by $H''=D''_1\setminus \mu_{2,b}(V)$.
        Then, for $1 \le \ell < k \le a_2$, we have $|\rsh_D(V)_{k;\ell}|=|\rsh_{D''}(H'')_{\ell;k}$.
    \end{enumerate}
  \end{corollary}

  In the results below, we keep the notation and assumptions from Corollary~\ref{cor:remote shadows}.
  It follows that, for $H\subset D_1$ and $1 \le d < j \le a_1$, we may define an order-reversing bijection $\theta^H_{j;d} : \rsh_D(H)_{j;d} \to \rsh_{D'}(V')_{d;j}$.
  Similarly, for $V\subset D_2$ and $1 \le \ell < k \le a_2$, we may define an order-reversing bijection $\theta^V_{k;\ell} : \rsh_D(V)_{k;\ell} \to \rsh_{D''}(H'')_{\ell;k}$.
  \begin{definition}\mbox{}
    \begin{enumerate}
      \item For $H\subset D_1$ and $V \subset \rsh_D(H)$, define $\Omega_H(V) \subset \rsh_{D'}(V')$ by
        \[\Omega_H(V)=\{\theta^H_{j;d}(v) : v \in \rsh_D(H)_{j;d}, 1 \le d < j \le a_1\}.\]
      \item For $V\subset D_2$ and $H \subset \rsh_D(V)$, define $\Omega_V(H) \subset \rsh_{D''}(H'')$ by
        \[\Omega_V(H)=\{\theta^V_{k;\ell}(h) : h \in \rsh_D(V)_{k;\ell}, 1 \le \ell < k \le a_2\}.\]
    \end{enumerate}
  \end{definition}

  \begin{lemma}\mbox{}
    \begin{enumerate}
      \item Consider $H\subset D_1$ and $V \subset \rsh_D(H)$.
        Suppose $h'=\theta^H_{j;d}(v)$ for $v\in V$.
        Then $f_{\Omega_H(V)}(h'v'_d)=f_V(h_j v)$.
      \item Consider $V\subset D_2$ and $H \subset \rsh_D(V)$.
        Suppose $v''=\theta^V_{k;\ell}(h)$ for $h\in H$.
        Then $f_{\Omega_V(H)}(h''_\ell v'')=f_V(h v_k)$.
    \end{enumerate}
  \end{lemma}

  The following equivalence of compatibilities is the main result we need.
  \begin{corollary}\mbox{}
    \begin{enumerate}
      \item For $H \subset D_1$ and $V \subset \rsh_D(H)$, we have $V\in\cC_D(H)$ if and only if $\Omega_H(V)\in\cC_{D'}(V')$.
      \item For $V \subset D_2$ and $H \subset \rsh_D(V)$, we have $H\in\cC_D(V)$ if and only if $\Omega_V(H)\in\cC_{D''}(H'')$.
    \end{enumerate}
  \end{corollary}
